---
title: "User Avatar Bond Discrepancy Questionnaire"
author: "Taylor Brown"
date: '2022-04-06'
output: html_document
---

EFA completed via Jamovi - No syntax was used

First Step for CFA run packages if already installed 
```{r echo=FALSE, warning=FALSE, error=FALSE}
library (lavaan)
library(lavaanPlot)
library (semPlot)
library(semTools)
library(tidyverse)
library(psych)
library(psychTools)
```

Second - import the dataset and define model

```{r}
CFAdata<-haven::read_sav("Data.sav")%>%
  mutate_if(is.character, as.factor)
describe(CFAdata)
```

Specify the different models
```{r, echo=FALSE, warning=FALSE, error=FALSE}
onefactormodel <- "useravatar =~ W2_Dis1 + W2_Dis2 + W2_Dis6 + W2_Dis7 + W2_Dis8Rev + W2_Dis9 + W2_Dis10Rev + W2_Dis15Rev"
```

Fit the model and produce the results
```{r}
fit1 <- cfa(onefactormodel, data = CFAdata, estimator= "DWLS")

summary(fit1, fit.measures=TRUE, standardized=TRUE)
```

Produce the modification indices
```{r echo=FALSE, error=FALSE, warning=FALSE}
 

modificationindices(fit1, sort. = TRUE)

```

Produce the reliability indices
```{r echo=FALSE, error=FALSE, warning=FALSE}

semTools::reliability(fit1)

```

Graph the model via lavaan
```{r}
lavaanPlot(model = fit1, edge_options = list(color = "grey"))

```
Graph the model via semtools
```{r echo=FALSE, error=FALSE, warning=FALSE}
semPaths(fit1, whatLabels = "std", layout = "tree2", rotation = 2, sizeLat = 12, sizeInt = 5, sizeMan2 = 5, shapeMan = "square", shapeLat = "circle",node.width = 0.6, asize = 3, edge.label.cex = 0.75, fade = F)

```

#To Repeat the procedure with a different estimator, change the estimator (ML).


After having confirmed the model, we will proceed with the IRT
Step 1 pachages run (if aleardy installed)

```{r echo=FALSE, warning=FALSE, error=FALSE}
#install.packages("mirt")
#install.packages("naniar")
#install.packages("Rcpp")
library(mirt)
library(naniar)
library(Rcpp)

```


Define data
```{r}
data<-haven::read_sav("Data.sav")%>%
  mutate_if(is.character, as.factor)
describe(data)
view(data)

```
Then we select only the variables we need for our analysis
```{r}
myvars <- c("W2_Dis1", "W2_Dis2", "W2_Dis6", "W2_Dis7", "W2_Dis8Rev", "W2_Dis9", "W2_Dis10Rev", "W2_Dis15Rev"
)
data1<-data[myvars]
describe(data1)
```


re-view data and define the scale
```{r}
glimpse(data1)

scale <-(data1)

head(scale, 8) 

```

Fit the graded response model using the 'mirt' R package.
```{r echo=FALSE, warning=FALSE, error=FALSE}

mod1 <- (mirt(scale, 1, verbose = FALSE, itemtype = 'graded', SE = TRUE))

M2(mod1, type = "C2", calcNull = FALSE, na.rm = TRUE)

```


```{r echo=TRUE, error=FALSE, warning=FALSE}

itemfit(mod1, na.rm = TRUE)

```

Examine IRT parameters 
(0 = non discriminative; 0.01–0.34 = very low; 0.35–0.64 = low; 0.65–1.34 = moderate; 1.35–1.69 = high; >1.70 = very high; Baker, 2001)

```{r echo=FALSE, error=FALSE, warning=FALSE}

IRT_parms <- coef(mod1, IRTpars = TRUE, simplify = TRUE, na.rm=TRUE)
IRT_parms$items

```

Examine items parameters/loadings and communalities

```{r}

summary(mod1)

```

Produce IRT plots - Category characteristic Curve
```{r plot1, echo=FALSE, warning=FALSE, error=FALSE}

plot(mod1, type='trace', which.item = c(1,2,3,4,5,6,7,8), facet_items=T, 
     as.table = TRUE, auto.key=list(points=F, lines=T, columns=4, space = 'top', cex = .8), 
     theta_lim = c(-3, 3), 
     main = "")


```


Produce the Item information Curves
```{r plot2, echo=FALSE, error=FALSE, warning=FALSE}

plot(mod1, type='infotrace', which.item = c(1,2,3,4,5,6,7,8), facet_items=T, 
     as.table = TRUE, auto.key=list(points=F, lines=T, columns=1, space = 'right', cex = .8), 
     theta_lim = c(-3, 3), 
     main="")

```

Scale information and conditional standard errors
```{r plot3, echo=FALSE}

plot(mod1, type = 'infoSE', theta_lim = c(-3, 3), 
     main="")

```

Produce the Conditional reliability if chosen
```{r plot4, echo=FALSE}

plot(mod1, type = 'rxx', theta_lim = c(-3, 3), 
     main="" )

## Single IRT reliability is also produced ##

marginal_rxx(mod1)


```

Scale characteristic Curve
```{r plot5, echo=FALSE}

plot(mod1, type = 'score', theta_lim = c(-3, 3), main = "")

```



# THE END



